Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-05-24 fully-abstract-comp/technical-report.tex

%%% Instruction formatting
\newcommand{\sourcecolortext}{blue}
\newcommand{\sourcecolor}[1]{\color{blue}}
\newcommand{\src}[1]{{\sourcecolor{} #1}}
\newcommand{\targetcolortext}{green}
\newcommand{\targetcolor}[1]{\color{green}}
\newcommand{\trg}[1]{{\targetcolor{} #1}}

@@

% Two arguments
\newcommand{\tjnz}[2]{\twoinstr{\trg{jnz}}{#1}{#2}}
\newcommand{\tisptr}[2]{\twoinstr{\trg{isptr}}{#1}{#2}}
\newcommand{\tgeta}[2]{\twoinstr{\trg{geta}}{#1}{#2}}
\newcommand{\tgetb}[2]{\twoinstr{\trg{getb}}{#1}{#2}}
\newcommand{\tgete}[2]{\twoinstr{\trg{gete}}{#1}{#2}}
\newcommand{\tgetp}[2]{\twoinstr{\trg{getp}}{#1}{#2}}
\newcommand{\tgetl}[2]{\twoinstr{\trg{getl}}{#1}{#2}}
\newcommand{\tmove}[2]{\twoinstr{\trg{move}}{#1}{#2}}
\newcommand{\tstore}[2]{\twoinstr{\trg{store}}{#1}{#2}}
\newcommand{\tload}[2]{\twoinstr{\trg{load}}{#1}{#2}}
\newcommand{\tlea}[2]{\twoinstr{\trg{lea}}{#1}{#2}}

@@

%%% Updates
\newcommand{\update}[2]{[#1 \mapsto #2]}
\newcommand{\updReg}[3][\Phi]{#1\update{\sreg.#2}{#3}}
\newcommand{\updPc}[2][\Phi]{\updReg[#1]{\pcreg}{#2}}

%%% Source dom
\newcommand{\sourcedom}[1]{\mathrm{#1}}
\newcommand{\sRegName}{\sourcedom{RegisterName}}
\newcommand{\sAddr}{\sourcedom{Addr}}
\newcommand{\sPerm}{\sourcedom{Perm}}
\newcommand{\sCap}{\sourcedom{Cap}}
\newcommand{\sWord}{\sourcedom{Word}}
\newcommand{\sMem}{\sourcedom{Memory}}
\newcommand{\sReg}{\sourcedom{RegisterFile}}
\newcommand{\sStk}{\sourcedom{Stack}}
\newcommand{\sConf}{\sourcedom{Conf}}
\newcommand{\sExecConf}{\sourcedom{ExecConf}}
\newcommand{\sGlobal}{\sourcedom{Global}}
\newcommand{\sMemSeg}{\sourcedom{MemorySegment}}
\newcommand{\sStkFrame}{\sourcedom{StackFrame}}
\newcommand{\sStack}{\sourcedom{Stack}}

\newcommand{\smem}{\sourcedom{mem}}
\newcommand{\sreg}{\sourcedom{reg}}
\newcommand{\sstk}{\sourcedom{stk}}
\newcommand{\smsstk}{\sourcedom{ms_{stk}}}
\newcommand{\sstkframe}{\sourcedom{frame}}
\newcommand{\sopc}{\sourcedom{opc}}
\newcommand{\sastk}{\sourcedom{a_{stk}}}
\newcommand{\sperm}{\sourcedom{perm}}
\newcommand{\sgl}{\sourcedom{g}}
\newcommand{\sbase}{\sourcedom{base}}
\newcommand{\send}{\sourcedom{end}}
\newcommand{\saddr}{\sourcedom{a}}
\newcommand{\scap}{\sourcedom{c}}
\newcommand{\sms}{\sourcedom{ms}}

\newcommand{\stkptr}[4]{\sourcedom{stack\text{-}ptr}(#1,#2,#3,#4)}
\newcommand{\retptr}{\sourcedom{ret\text{-}ptr}}

@@

%%% Named registers
\newcommand{\pcreg}{\mathrm{pc}}
\newcommand{\rstk}{\mathrm{r}_\mathrm{stk}}
\newcommand{\rO}{\mathrm{r}_\mathrm{ret}}

@@

\begin{document}
\section{TODO}
\begin{itemize}
\item Linking
\item Component
\item Cross-language LR
\end{itemize}

\section{The two capability machines}
\subsection{Domains}
Source language domains:
\[
  \begin{array}{rrcl}
   \saddr,\sbase \in & \sAddr & \defeq & \nats \\
    &\sWord & \defeq & \ints \uplus \sCap\\
   \sperm \in& \sPerm & \defbnf & \dots \\
    \sgl \in&\sGlobal & \defbnf & \glob \mid \local \\
    &\sCap &::= & \left\{((\sperm,\sgl),\sbase,\send,\saddr) \mid \send \in \sAddr \cup \{\infty\}\right\} {\sourcecolor{} \uplus}\\
    & & & {\sourcecolor{} \{ \stkptr{\sperm}{\sbase}{\send}{\saddr} \}\uplus}\\ 
    & & & {\sourcecolor{} \{ \retptr \}}\\ 
    &\sRegName & \defbnf &\pcreg \mid \rO \mid \rstk \mid \dots \\
    &\sReg & \defeq & \sRegName \fun \sWord\\
    & \sMem & \defeq & \sAddr \fun \sWord \\
    & \sMemSeg & \defeq & \sAddr \parfun \sWord \\
    {\sourcecolor{} \sstkframe \in} & {\sourcecolor{} \sStkFrame} & {\sourcecolor{} \defeq} & {\sourcecolor{} \sCap \times \sMemSeg \times \sAddr}\\
    {\sourcecolor{} \sstk \in}& {\sourcecolor{} \sStack} & {\sourcecolor{} \defeq} & {\sourcecolor{} \sStkFrame^*} \\
    \Phi \in & \sExecConf & \defeq & \sMem \times \sReg {\sourcecolor{} \; \times \; \sStack \times \sMemSeg }\\
    &\sConf & \defeq & \sExecConf \uplus \{\failed\} \uplus (\{\halted\} \times \sMem)
  \end{array}
\]
The target language domains are all the non blue parts in the above.

More convenient definitions
\[
  \begin{array}{rcl}
    \Phi(r) & \defeq & \Phi.\sreg(r)
  \end{array}
\]
where $r\in \sRegName$

\subsection{Syntax}
The target machine is[dashed] a simple capability machine with memory capabilities, local capabilities and enter capabilities. The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &::= &  \trg{r} \mid n \\
\trg{i} &::= & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetl{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tlea{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tsubseg{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \\
      & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}}
\end{array}
\]

The source machine is also a capability machine with memory capabilities, local capabilities and enter capabilities. Unlike the target machine, the source machine is going to have a built in stack. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    n & \in & \nats \\
    \src{r} &\in &  \sRegName \setminus \{\rO,\rstk\}\\
    \src{\rn} &::= & \src{r} \mid n \\
    \src{i} & ::= &  \trg{i} \mid \scall{\src{r}}{\src{\rn}}
  \end{array}
\]
There is one suntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{}{}$ instruction.
\subsection{Permissions}
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}[main node/.style={}]
    \node[main node] (rwlx) {$\rwlx$};
    \node[main node] (rwx) [below of=rwlx] {$\rwx$};
    \node[main node] (rx) [below of=rwx] {$\rx$};
    \node[main node] (e) [below of=rx] {$\enter$};

@@

\subsubsection{Source Language}

\begin{align*}
  \ssem{\sjmp{r}} = & 
    \begin{cases}
      \Phi
      \begin{aligned}[t]
        & \update{\sreg.\pcreg}{\opc} \\
        & \update{\smsstk}{\ms_\stk' \uplus \clearms{\ms_\stk}}\\
        & \update{\sastk}{a_\stk'}\\
        & \update{\sstk}{\stk'}
      \end{aligned} & \Phi(r) = \retptr \text{ and }
      \Phi.\sstk = (\opc,\ms_\stk',a_\stk') :: \stk'\\
      & \\
      \updPc{\updPcPerm{\Phi(r)}} & \text{otherwise}
    \end{cases} \\
\end{align*}
\begin{align*}
  \ssem{\scall{r}{\rn}} = & 
    \begin{cases}
      (\mem,\reg',\stk',\ms_\stk') & \Phi = (\mem,\reg,\stk,\ms_\stk) \text{ and }\\
      \\
      \failed & \text{otherwise}
    \end{cases}
\end{align*}

@@

The context with $r1$ as an executable capability pointing to:
\begin{lstlisting}
$\scall{r5}{0}$
$\sjmp{r5}$
\end{lstlisting}
distinguishes the two contexts, but two instructions are not enough to do the same at the target level. We would not have enough instructions to set up a proper return pointer for the compiled return to use.

>>>>

%%% Instruction formatting
\newcommand{\sourcecolortext}{blue}
\newcommand{\sourcecolor}[1]{\color{blue}}
\newcommand{\src}[1]{{\sourcecolor{} #1}}
\newcommand{\targetcolortext}{black}
\newcommand{\targetcolor}[1]{\color{black}}
\newcommand{\trg}[1]{{\targetcolor{} #1}}

@@

% Two arguments
\newcommand{\tjnz}[2]{\twoinstr{\trg{jnz}}{#1}{#2}}
\newcommand{\tisptr}[2]{\twoinstr{\trg{isptr}}{#1}{#2}}
\newcommand{\tgeta}[2]{\twoinstr{\trg{geta}}{#1}{#2}}
\newcommand{\tgetb}[2]{\twoinstr{\trg{getb}}{#1}{#2}}
\newcommand{\tgete}[2]{\twoinstr{\trg{gete}}{#1}{#2}}
\newcommand{\tgetp}[2]{\twoinstr{\trg{getp}}{#1}{#2}}
\newcommand{\tgetl}[2]{\twoinstr{\trg{getl}}{#1}{#2}}
\newcommand{\tmove}[2]{\twoinstr{\trg{move}}{#1}{#2}}
\newcommand{\tstore}[2]{\twoinstr{\trg{store}}{#1}{#2}}
\newcommand{\tload}[2]{\twoinstr{\trg{load}}{#1}{#2}}
\newcommand{\tlea}[2]{\twoinstr{\trg{lea}}{#1}{#2}}
\newcommand{\txjmp}[2]{\twoinstr{\trg{xjmp}}{#1}{#2}}
\newcommand{\tcseal}[2]{\twoinstr{\trg{cseal}}{#1}{#2}}

@@

%%% Updates
\newcommand{\update}[2]{[#1 \mapsto #2]}
\newcommand{\updReg}[3][\Phi]{#1\update{\reg.#2}{#3}}
\newcommand{\updPc}[2][\Phi]{\updReg[#1]{\pcreg}{#2}}

%%% Source dom
\newcommand{\shareddom}[1]{\mathrm{#1}}
\newcommand{\RegName}{\shareddom{RegisterName}}
\newcommand{\Addr}{\shareddom{Addr}}
\newcommand{\Seal}{\shareddom{Seal}}
\newcommand{\Perm}{\shareddom{Perm}}
\newcommand{\Caps}{\shareddom{Cap}}
\newcommand{\SealableCaps}{\shareddom{SealableCap}}
\newcommand{\Word}{\shareddom{Word}}
\newcommand{\Mem}{\shareddom{Memory}}
\newcommand{\Reg}{\shareddom{RegisterFile}}
\newcommand{\Stk}{\shareddom{Stack}}
\newcommand{\Conf}{\shareddom{Conf}}
\newcommand{\ExecConf}{\shareddom{ExecConf}}
\newcommand{\Global}{\shareddom{Global}}
\newcommand{\MemSeg}{\shareddom{MemorySegment}}
\newcommand{\StkFrame}{\shareddom{StackFrame}}
\newcommand{\Stack}{\shareddom{Stack}}

\newcommand{\scbnf}{\shareddom{sc}}
\newcommand{\cbnf}{\shareddom{c}}
\newcommand{\permbnf}{\shareddom{perm}}
\newcommand{\addrbnf}{\shareddom{a}}
\newcommand{\basebnf}{\shareddom{base}}
\newcommand{\aendbnf}{\shareddom{end}}
\newcommand{\glbnf}{\shareddom{gl}}
\newcommand{\sealbasebnf}{\sigma_\shareddom{base}}
\newcommand{\sealendbnf}{\sigma_\shareddom{end}}

\newcommand{\sstk}{\shareddom{stk}}
\newcommand{\smsstk}{\shareddom{ms_{stk}}}
\newcommand{\sstkframe}{\shareddom{frame}}
\newcommand{\sopc}{\shareddom{opc}}
\newcommand{\sastk}{\shareddom{a_{stk}}}
\newcommand{\perm}{\shareddom{perm}}
\newcommand{\gl}{\shareddom{g}}
\newcommand{\base}{\shareddom{base}}
\newcommand{\aend}{\shareddom{end}}
\newcommand{\addr}{\shareddom{a}}
\newcommand{\scap}{\shareddom{c}}
\newcommand{\sms}{\shareddom{ms}}

\newcommand{\stkptr}[1]{\mathrm{stack\text{-}ptr}(#1)}
\newcommand{\retptr}{\mathrm{ret\text{-}ptr}}
\newcommand{\retptrd}{\mathrm{ret\text{-}ptr\text{-}data}}
\newcommand{\retptrc}{\mathrm{ret\text{-}ptr\text{-}code}}

\newcommand{\seal}[1]{\shareddom{seal}(#1)}
\newcommand{\sealed}[1]{\shareddom{sealed}(#1)}

@@

%%% Named registers
\newcommand{\pcreg}{\mathrm{pc}}
\newcommand{\rstk}{\mathrm{r}_\mathrm{stk}}
\newcommand{\rO}{\mathrm{r}_\mathrm{ret}}
\newcommand{\rret}{\rO}
\newcommand{\rdata}{\mathrm{r}_\mathrm{data}}

@@

\begin{document}
\section{The two capability machines}
\subsection{Domains}
Source language domains:
\[
  \begin{array}{rrcl}
   \addrbnf,\basebnf \in & \Addr & \defeq & \nats \\
    \sealbasebnf, \sigma \in & \Seal & \defeq & \nats \\
    &\Word & \defeq & \ints \uplus \Caps\\
    \permbnf \in& \Perm & \defbnf & \dots \\
    &\glbnf & \defbnf & \glob \mid \local \\
    & \aendbnf & \in & \Addr \uplus \{\infty \} \\
    &  \sealendbnf & \in & \Seal \uplus \{\infty \} \\
    &\scbnf &\defbnf & ((\permbnf,\glbnf),\basebnf,\aendbnf,\addrbnf) \mid \seal{\glbnf,\sealbasebnf,\sealendbnf}\\
    & & & {\sourcecolor{} \mid \stkptr{\permbnf,\basebnf,\aendbnf,\addrbnf}}\\     &\cbnf & \defbnf &  \scbnf \mid \sealed{\scbnf,\sigma}{\sourcecolor{} \; \mid \retptrd \mid \retptrc}\\ 
    &\RegName & \defbnf &\pcreg \mid \rO \mid \rstk \mid \rdata \mid \dots \\
    &\Reg & \defeq & \RegName \fun \Word\\
    &\Mem & \defeq & \Addr \fun \Word \\
    &\MemSeg & \defeq & \Addr \parfun \Word \\
    {\sourcecolor{} \sstkframe \in} & {\sourcecolor{} \StkFrame} & {\sourcecolor{} \defeq} & {\sourcecolor{} \Caps \times \MemSeg \times \Addr}\\
    {\sourcecolor{} \sstk \in}& {\sourcecolor{} \Stack} & {\sourcecolor{} \defeq} & {\sourcecolor{} \StkFrame^*} \\
    \Phi \in & \ExecConf & \defeq & \Mem \times \Reg {\sourcecolor{} \; \times \; \Stack \times \MemSeg }\\
    &\Conf & \defeq & \ExecConf \uplus \{\failed\} \uplus (\{\halted\} \times \Mem)
  \end{array}
\]
The target language domains are all the non blue parts in the above. The source language domains are the black and blue parts in the above. Further
\begin{itemize}
\item $\glbnf$ defines domain $\Global$
\item $\scbnf$ defines domain $\SealableCaps$
\item $\cbnf$ defines domain $\Caps$
\end{itemize}

More convenient definitions
\[
  \begin{array}{rcl}
    \Phi(r) & \defeq & \Phi.\reg(r)
  \end{array}
\]
where $r\in \RegName$

\subsection{Syntax}
The target machine is a simple capability machine with memory capabilities, local capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle} (Inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &::= &  \trg{r} \mid n \\
\trg{i} &::= & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetl{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tlea{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tsubseg{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \\
      & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}} \mid \txjmp{r}{r} \mid \tcseal{r}{r}
\end{array}
\]

The source machine is also a capability machine with memory capabilities, local capabilities and sealed capabilities. Unlike the target machine, the source machine is going to have a built in stack along with special stack and return capabilities. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    n & \in & \nats \\
    \src{r} &\in &  \RegName \setminus \{\rO,\rstk\}\\
    \src{\rn} &::= & \src{r} \mid n \\
    \src{i} & ::= &  \trg{i} \mid \scall{\src{r}}{\src{r}}
  \end{array}
\]
There is one syntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{}{}$ instruction.

\subsection{Permissions}
\lau{23-03-2017: I am not sure we need the opaque capabilities anymore.}
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}[main node/.style={}]
    \node[main node] (rwlx) {$\rwlx$};
    \node[main node] (rwx) [below of=rwlx] {$\rwx$};
    \node[main node] (rx) [below of=rwx] {$\rx$};
    \node[main node] (e) [below of=rx] {$\enter$};

@@

\subsubsection{Source Language}
\lau{23-03-2017: $\sjmp{}$ and $\scall{}{}$ needs an update.}
\begin{align*}
  \ssem{\sjmp{r}} = & 
    \begin{cases}
      \Phi
      \begin{aligned}[t]
        & \update{\reg.\pcreg}{\opc} \\
        & \update{\smsstk}{\ms_\stk' \uplus \clearms{\ms_\stk}}\\
        & \update{\sastk}{a_\stk'}\\
        & \update{\sstk}{\stk'}
      \end{aligned} & \Phi(r) = \retptr \text{ and }
      \Phi.\sstk = (\opc,\ms_\stk',a_\stk') :: \stk'\\
      & \\
      \updPc{\updPcPerm{\Phi(r)}} & \text{otherwise}
    \end{cases} \\
\end{align*}
\begin{align*}
  \ssem{\scall{r_1}{r_2}} = & 
    \begin{cases}
      (\mem,\reg',\stk',\ms_\stk') & \Phi = (\mem,\reg,\stk,\ms_\stk) \text{ and }\\
      \\
      \failed & \text{otherwise}
    \end{cases}
\end{align*}
\begin{itemize}
\item $\scall{}{}$ does not do argument spilling anymore. We leave it to the caller to push the arguments for spilling to the stack and update the stack pointer accordingly.
\end{itemize}

@@

The context with $r1$ as an executable capability pointing to:
\begin{lstlisting}
$\scall{r5}{0}$
$\sjmp{r5}$
\end{lstlisting}
\footnote{At this time $\scall{}{}$ did argument spilling and it only takes one argument because we were considering enter capabilities.}distinguishes the two contexts, but two instructions are not enough to do the same at the target level. We would not have enough instructions to set up a proper return pointer for the compiled return to use.

### 2017-05-24 local-capability-machine/local-capability-machine.tex

\subsection{Variant of the ``awkward'' example}
Assembly variant of the ``awkward'' example from \citep[p.~11]{Dreyer:2010:IHS:1863543.1863566} which roughly was:
\begin{verbatim}
g = fun _ => let x = 0 in
               fun f =>
                 x := 0;
                 f();
                 x := 1;
                 f();
                 assert(x == 1)
\end{verbatim}
Our translation of the example:
\begin{lstlisting}
g1:  malloc $r_2$ 1
     store $r_2$ 0
     move $\pcreg$ $r_3$
     lea $r_3$ $\dots$
     crtcls $[(x, r_2)]$ $r_3$
     rclear $\RegName \setminus \{\pcreg,r_0,r_1 \}$
1g:  jmp $r_0$
f4:  reqglob $r_1$
     prepstack $r_\stk$
     store $x$ 0
     scall $r_1$($[]$,$[r_0,r_1,r_{\var{env}}]$)
     store $x$ 1
     scall $r_1$($[]$,$[r_0,r_{\var{env}}]$)
     load $r_1$ x
     assert $r_1$ 1
     mclear $r_\stk$
     rclear $\RegName \setminus \{r_0,\pcreg\}$
4f:  jmp $r_0$
\end{lstlisting}
Where the $\dots$ is the appropriate offset to make the capability point to \texttt{f4}.

>>>>

\subsection{Variant of the ``awkward'' example}
Assembly variant of the ``awkward'' example from \citep[p.~11]{Dreyer:2010:IHS:1863543.1863566} which roughly was:
\begin{verbatim}
g = fun _ => let x = 0 in
               fun f =>
                 x := 0;
                 f();
                 x := 1;
                 f();
                 assert(x == 1)
\end{verbatim}
Our translation of the example:
\begin{lstlisting}
g1:  malloc $r_2$ 1
     store $r_2$ 0
     move $r_3$ $\pcreg$
     lea $r_3$ $\dots$
     crtcls $[(x, r_2)]$ $r_3$
     rclear $\RegName \setminus \{\pcreg,r_0,r_1 \}$
1g:  jmp $r_0$
f4:  reqglob $r_1$
     prepstack $r_\stk$
     store $x$ 0
     scall $r_1$($[]$,$[r_0,r_1,r_{\var{env}}]$)
     store $x$ 1
     scall $r_1$($[]$,$[r_0,r_{\var{env}}]$)
     load $r_1$ x
     assert $r_1$ 1
     mclear $r_\stk$
     rclear $\RegName \setminus \{r_0,\pcreg\}$
4f:  jmp $r_0$
\end{lstlisting}
Where the $\dots$ is the appropriate offset to make the capability point to \texttt{f4}.
